Calculating Entropies With Nested Sampling

### 2017-02-27 paper/ms.tex
Included the figure

>>>>

\begin{figure}[!ht]
\centering
\includegraphics[width=0.5\linewidth]{figures/algorithm.pdf}
\caption{To evaluate the log-probability (or density) of the blue
probability distribution at the red point, Nested Sampling can be used,
with the blue distribution plays the role of the ``prior'' in NS, and the
Euclidian distance from the red point (illustrated with red contours)
is the ``likelihood''.\label{fig:algorithm}}
\end{figure}
